\def\moduleCode{COMP240}
\def\moduleName{Game Development I: Production}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Dr Michael Scott}
\def\academicStaff{Brian McDonald (Moderator)}

\def\introduction{This module allows you to work on a game development project over its course. You will develop your knowledge of computing for games in a practical way, using techniques and methods that help you to take a creative approach to building an innovative product or solution to a game development challenge. Further to this, you will reflect more deeply upon the commercial prospects of your project.}

\def\moduleAims{
	{Understand the design and implementation of innovative software products targeted at the games industry},
	{Consolidate your knowledge of game development practices and software engineering over a longer project period},
	{Understand markets and business models associated with the games industry}}
	
\def\moduleLearningOutcomes{1,2,3,4,5,6}
	
\def\assessmentCriteria{
	{Apply principles of computing creatively to build iteratively an effective computing solution relevant to the development of games.},
	{Communicate clearly and appropriately when working in a group.},
	{Analyse critically the strengths and weaknesses of your interactions. Work iteratively on the basis on on-going evaluation to produce an appropriate solution.},
	{Create a solution for which there is a market and for which you can demonstrate need.},
	{Leverage research to produce an innovative solution.},
	{Make use of a range of methods to organise and execute a computing solution and meet deadlines, plan and organise your work flow effectively.}}

\def\assignments{
	{Market Evaluation \& Business Case, 30\%},
	{Production Tasks, 40\%},
	{Project Pitches, 10\%},
	{CPD Tasks, 20\%}}

\def\hours{
	{Sessions, 24 hours},
	{Supervised Studio Practice, 30 hours},
	{Directed Reading, 18 hours},
	{Market Evaluation \& Business Case, 21 hours},
	{Production Tasks, 28 hours},
	{Demo Preparation, 7 hours},
	{CPD Tasks, 14 hours},
	{Self-Directed Study, 18 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{3268}