\def\moduleCode{COMP350}
\def\moduleName{Algorithms \& Optimisation}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Brian McDonald}
\def\academicStaff{Dr Edward Powley (Moderator)}

\def\introduction{On this module you practise and develop your computing skills but focusing on methods for creating efficient and optimised code. You will learn methods of resource management required within the context of games. You will acquire greater knowledge of how savings can be made and how to trade-off various elements to create optimisation. You will grow in your understanding and experience of how to predict outcomes of various approaches and how to evaluate possible strategies requisite for professional practice. A port project will enable you to tackle in a live situation some of the problems of efficiency and optimisation that arise.}

\def\moduleAims{
	{Gain in understanding of techniques used professionally in the management of computing resources.},
	{Acquire knowledge and experience of concepts used to predict and model resource use.},
	{Acquire the knowledge and experience to enable critical evaluation of trade-offs to generate optimisation and efficiency.}}
	
\def\moduleLearningOutcomes{1,3,6}
	
\def\assessmentCriteria{
	{Apply professional approach to resource management in the context of constraint.},
	{},
	{Profile algorithms to make informed and effective choices about trade-offs to ensure optimisation and efficiency.},
	{},
	{},
	{Meet deadlines by planning available time effectively plan and manage time to produce a solution efficiently and by the deadline.}}

\def\assignments{
	{Optimisation Task, 50\%},
	{Porting Task, 30\%},
	{Research Journal, 20\%}}

\def\hours{
	{Sessions, 27 hours},
	{Directed Reading, 18 hours},
	{Optimisation Task, 36 hours},
	{Porting Task, 20 hours},
	{Port Changes to Collaborative Game, 20 hours},
	{Research Journal, 15 hours},
	{Self-Directed Study, 24 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{???}