\def\moduleCode{COMP340}
\def\moduleName{Game Development II: Production}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Dr Michael Scott}
\def\academicStaff{Brian McDonald (Moderator)}

\def\introduction{You will consolidate your multi-disciplinary collaborative game development experience to work on a substantial development project over the course of two study blocks. You will develop your knowledge of computing for games in a practical way using techniques and methods that help you to take a creative approach to building an innovative and marketable game. This second module focuses on the production and launch of your game.}

\def\moduleAims{
	{Consolidate your knowledge and experience in the context of creating a professional, innovative computing solution in a collaborative context.},
	{Consolidate knowledge and experience of how to independently organise and execute a computing project over a longer period and in a collaborative context.},
	{Demonstrate independence in identifying a problem that requires a solution and work iteratively and collaboratively towards that solution.}}
	
\def\moduleLearningOutcomes{1,2,3,4,5,6}
	
\def\assessmentCriteria{
	{Apply computing principles and processes to produce collaboratively an effective computing solution of use within a game development context.},
	{Communicate clearly and appropriately when working in a group.},
	{Work iteratively on the basis of on-going evaluation in a collaborative context and analyse critically the strengths and weaknesses of your collaborative iterations.},
	{Create a solution for which there is a market and for which you can show need.},
	{Create an innovative solution tailored to a known market appropriate to platform.},
	{Understand and use effectively methods for organising and executing a game development project in a collaborative context. Show an understanding of how to plan, organise and execute a substantial, collaborative project.}}

\def\assignments{
	{Market Evaluation \& Business Case, 30\%},
	{Production Tasks, 40\%},
	{Collaborative Game Demo, 10\%},
	{CPD Tasks, 20\%}}

\def\hours{
	{Sessions, 24 hours},
	{Supervised Studio Practice, 33 hours},
	{Directed Reading, 12 hours},
	{Market Evaluation \& Business Case, 14 hours},
	{Production Tasks, 44 hours},
	{Pitch Preparation, 7 hours},
	{CPD Tasks, 14 hours},
	{Self-Directed Study, 12 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{3031}