\def\moduleCode{COMP110}
\def\moduleName{Principles of Computing}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Dr Edward Powley}
\def\academicStaff{Dr Michael Scott (Moderator)}

\def\introduction{This module introduces you to the basic principles of computing in the context of digital games. It is designed to complement the other modules, providing a broad foundation on the theories, methods, models, and techniques in computing which will help you to construct computer programs and be able to make use of relevant scholarly sources.}

\def\moduleAims{
	{Understand the basic principles, terminology, roles, and software development concept that computing professionals apply within a game development context},
	{Understand how to apply computing theory to practical programming activities},
	{Understand how to conduct basic software development tasks}}
	
\def\moduleLearningOutcomes{1,2,3,4,6}
	
\def\assessmentCriteria{
	{Demonstrate a basic understanding of computing fundamentals. Apply basic knowledge and understanding of the techniques used in software development. Understand the creative value of maker-style and iterative approaches for the generation of innovation.},
	{Show a basic understanding of how to communicate effectively with stakeholders in writing, verbally, and through adherence to coding standards. Annotate software to communicate with others effectively.},
	{Analyse critically the strengths and weaknesses of code and develop an ability to respond to the critical judgements of others.},
	{Research and explain the use of methodologies used in computing, apply knowledge to practice, and present that knowledge where appropriate in an academic format.},
	{},
	{Set goals and manage workloads to meet deadlines using set methodologies and present ideas in a variety of situations with appropriate support.}}

\def\assignments{
	{Worksheet Tasks, 80\%},
	{Research Journal, 20\%}}

\def\hours{
	{Sessions, 36 hours},
	{Directed Reading, 18 hours},
	{Worksheet Tasks, 56 hours},
	{Research Journal, 14 hours},
	{Self-Directed Study, 36 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{1249}