\moduleCode{COMP150}
\moduleName{Game Development Practice}
\credits{20}
\isCompulsory{Compulsory}

\moduleLeader{Dr Michael Scott}
\def\academicStaff{Dr Edward Powley (Moderator), Brian McDonald (Moderator)}

\def\introduction{This module is designed to introduce you to the foundational principles and processes of professional game development. You will gain an understanding of the way that different components come together to make playable games and how those components are organised through the development pipeline. You will also gain a 'first principles' understanding of how games are designed with a target market in mind, how a strong underlying concept is developed, and how different aspects of creative computing contribute to the process.}

\def\moduleAims{
	{Understand the basic principles, terminology, roles, tools, and software used in the development of digital games},
	{Apply foundational knowledge and skills in order to organise and execute a game development project},
	{Understand how to manage a collective game development project and communicate effectively within the development group}}
	
\def\moduleLearningOutcomes{1,2,3,4,5,6}
	
\def\assessmentCriteria{
	{Apply basic knowledge and understanding of the professional techniques used to create digital games and employ elementary principles of game development to devise a simple game concept using Agile and iterative methods.},
	{Organise your ideas and material to communicate clearly with others; have a working knowledge of Agile methods.},
	{Identify and appraise the main strengths and weakness of your working methods and solutions.},
	{Research uses of Agile methods and supports within the context of game development.},
	{Show a basic understanding of the commercial and enterprise context of the games industry and the professional qualities needed for decision-making within that context.},
	{Deliver a collective game concept on time and to brief, responding appropriately to problems and changes in direction. Choose appropriate means to convey your development ideas.}}

\def\assignments{
	{Agile Essay, 30\%},
	{Pre-Production Tasks, 40\%},
	{Game Design Pitches, 10\%},
	{CPD Tasks, 20\%}}

\def\hours{
	{Sessions, 36 hours},
	{Supervised Studio Practice, 42 hours},
	{Directed Reading, 12 hours},
	{Agile Essay, 21 hours},
	{Pre-Production Tasks, 28 hours},
	{Game Design \& Pitch Preparation, 7 hours},
	{CPD Tasks, 14 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{1090}