\def\moduleCode{COMP260}
\def\moduleName{Distributed Systems}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Brian McDonald}
\def\academicStaff{Dr Michael Scott (Moderator)}

\def\introduction{This module will help you to gain a deeper understanding of distributed systems, computer networking, and database technology. You will learn about the use of these technologies in the context of games and further game practical experience of applying that learning to a collaborative development of a multi-player game.}

\def\moduleAims{
	{Gain in understanding of distributed systems through networking technology and databases},
	{Acquire knowledge and experience of networking and database technologies as applied to games},
	{Gain understanding and experience of how to apply networking and database technology in a specific game development context}}
	
\def\moduleLearningOutcomes{1,2,3,4,6}
	
\def\assessmentCriteria{
	{Work with the principles of networking, database, and parallel processing technology as applied to games and apply those technologies in a game development context.},
	{Demonstrate the ability to listen and understand what is required for a networking/database solution in a live development context. Ascertain the aims of a group’s game development concept to provide an appropriate networking or database solution.},
	{Analyse critically the strengths and weaknesses of your code and develop an ability to respond to the critical judgements of others.},
	{Demonstrate a working knowledge of distributed systems and their application to games. Apply that appropriately that knowledge to identify and create servers for a game.},
	{},
	{Show an understanding of how to plan and manage time. Meet deadlines by planning available time effectively.}}

\def\assignments{
	{Worksheet Tasks, 80\%},
	{Research Journal, 20\%}}

\def\hours{
	{Sessions, 36 hours},
	{Directed Reading, 18 hours},
	{Distributed Processing Task, 22 hours},
	{Client-Server Game Task, 34 hours},
	{Integration into Collaborative Game, 20 hours},
	{Research Journal, 12 hours},
	{Self-Directed Study, 18 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{1249}