\def\moduleCode{COMP230}
\def\moduleName{Game Development I: Pre-Production}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Dr Michael Scott}
\def\academicStaff{Alcywn Parker (Moderator)}

\def\introduction{This module forms the first part of a year-long game development project. You will consolidate your knowledge of computing for games in a practical way by applying techniques and methods to build a unique and innovative `indie'-style game. All the while, reflecting upon the professional and ethical implications of your working practice as well as the socio-cultural implications of the games that you design.}

\def\moduleAims{
	{Understand the design and implementation of innovative software products targeted at the games industry},
	{Consolidate your knowledge of game development practices and software engineering over a longer project period},
	{Understand the notion of professional practice and its ethical implications}}
	
\def\moduleLearningOutcomes{1,2,3,4,5,6}
	
\def\assessmentCriteria{
	{Apply principles of computing creatively to build iteratively an effective computing solution relevant to the development of games.},
	{Show a basic understanding of how to communicate effectively with stakeholders in writing, verbally and through adherence to coding standards. Annotate software to communicate with others effectively.},
	{Work iteratively on the basis of on-going evaluation and analyse critically the strengths and weaknesses of your iterations.},
	{Create a solution for which there is a market and for which you can show need. Research the platform and market for a solution.},
	{Based on research and iterative process produce an innovative solution.},
	{Make use of a range of methods to organise and execute a computing solution and meet deadlines, plan and organise your work flow effectively.}}

\def\assignments{
	{Ethics \& Professionalism Essay, 30\%},
	{Pre-Production Tasks, 40\%},
	{Project Pitches, 10\%},
	{CPD Tasks, 20\%}}

\def\hours{
	{Sessions, 24 hours},
	{Supervised Studio Practice, 30 hours},
	{Directed Reading, 18 hours},
	{Ethics \& Professionalism Essay, 21 hours},
	{Pre-Production Tasks, 28 hours},
	{Pitch Preparation, 7 hours},
	{CPD Tasks, 14 hours},
	{Self-Directed Study, 18 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{3026}