\def\moduleCode{COMP360}
\def\moduleName{Research Dissertation}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Dr Michael Scott}
\def\academicStaff{Dr Edward Powley (Moderator)}

\def\introduction{You will work on a major research project over the course of the year. You either work on empirical research relating to computing for games, or engage in practice-based research related to game development. This is an individual project so you can explore a topic or develop a solution in an area that interests you personally, but which also has a clearly identified market/industry need. This module forms the second part of your major research project and will equip you with knowledge of academic writing, information analysis and presentation, as well as research dissemination that you will then apply in the undertaking of the project.}

\def\moduleAims{
	{Consolidate understanding of generating innovative computing solutions at a professional level through a major project.},
	{Consolidate knowledge and experience of how to organise and execute a computing project over a longer period.},
	{Build on experience of methods used to identify a problem that requires a solution and work iteratively towards that solution.}}
	
\def\moduleLearningOutcomes{1,2,3,4,6}
	
\def\assessmentCriteria{
	{Apply principles of computing creatively to build iteratively an effective computing solution relevant to the development of games.},
	{Communicate in an academic format.},
	{Analyse critically the strengths and weaknesses of your iterations and work iteratively on the basis of on-going evaluation.},
	{Create a solution for which there is a market and for which you can show need.},
	{Create an innovative solution developed for a known target market.},
	{Make use of a range of methods to organise and execute a computing solution, meet deadlines, plan and organise your work flow effectively.}}

\def\assignments{
	{Research Artefact, 30\%},
	{Research Dissertation, 70\%}}

\def\hours{
	{Sessions, 24 hours},
	{Research Supervision, 4 hour},
	{Directed Reading, 12 hours},
	{Research Artefact, 20 hours},
	{Integration into Collaborative Game, 20 hours},
	{Research Dissertation, 40 hours},
	{Self-Directed Study, 40 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{???}