\def\moduleCode{COMP250}
\def\moduleName{Artificial Intelligence}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Dr Edward Powley}
\def\academicStaff{Dr Michael Scott (Moderator)}

\def\introduction{This module will help you to learn how AI is used in the context of games. You will gain in understanding and experience of the technical dimension of AI and how it might be used in the particular expressive context within game development. You will apply your learning in a practical context where you will design AI for a game in a live brief format, taking as your cue the game concepts developed by development teams across the academy.}

\def\moduleAims{
	{Gain in understanding of AI technology and techniques and their relation to games},
	{Acquire knowledge and experience of the expressive uses of AI in games contexts},
	{Apply AI solutions for specific game contexts}}
	
\def\moduleLearningOutcomes{1,2,3,4,6}
	
\def\assessmentCriteria{
	{Demonstrate an understanding of the technical principles of AI in a games context. Select and deploy appropriate AI techniques within the context of games development to create an expressive and appropriate solution.},
	{To communicate in a collaborative context to generate an innovative AI concept. Create AI for an existing game and generate an expressive and appropriate use of AI that communicates with its audience.},
	{Analyse critically the strengths and weaknesses of your code and develop an ability to respond to the critical judgements of others.},
	{Demonstrate a working knowledge of AI techniques literature and its application to games. Apply that appropriately that knowledge to identify and create AI for an expressive purpose.},
	{},
	{Show an understanding of how to plan and manage time. Meet deadlines by planning available time to deliver solution effectively.}}

\def\assignments{
	{Portfolio of AI Instances, 90\%},
	{Research Journal, 10\%}}

\def\hours{
	{Sessions, 36 hours},
	{Directed Reading, 18 hours},
	{Portfolio of AI Instances, 55 hours},
	{Integration into Collaborative Game, 20 hours},
	{Research Journal, 7 hours},
	{Self-Directed Study, 24 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{3027}