\def\moduleCode{COMP210}
\def\moduleName{Interfaces \& Interaction}
\def\credits{20}
\def\isCompulsory{Compulsory}

\def\moduleLeader{Alcwyn Parker}
\def\academicStaff{Dr Michael Scott (Moderator), Erik Gheelhoed (Guest Lecturer), Johnny Pope (Guest Lecturer)}

\def\introduction{On this module you will engage with interface technologies which are changing the way that we play games. You will undertake a series of practical and creative engagements with emergent technologies, such as augmented and virtual reality devices, working iteratively to produce an innovative solution. You may tie this work into either your individual or collaborative game development project.}

\def\moduleAims{
	{Gain in understanding of writing software of interface technologies},
	{Acquire knowledge of designing for a specific platform to create innovation.},
	{Develop understanding of managing an iterative development process}}
	
\def\moduleLearningOutcomes{1,2,3,4,6}
	
\def\assessmentCriteria{
	{Understand how to write software for AR/VR interfaces and how to design efficaciously for a specific platform.},
	{Communicate intention and context for a solution clearly and effectively. Present effectively your design and solution for an audience in pitch form.},
	{Analyse critically the strengths and weaknesses of your solution and development process. Make use of a range of methods to organise and execute a computing solution.},
	{Apply research in emergent interfaces and modes of interaction to the development of novel user interfaces.},
	{},
	{Show an understanding of how to plan and manage time and solution execution. Meet deadlines by planning available time to deliver solution effectively.}}

\def\assignments{
	{Interface Tasks, 30\%},
	{AR/VR Tasks, 60\%},
	{Research Journal, 10\%}}

\def\hours{
	{Sessions, 36 hours},
	{Directed Reading, 18 hours},
	{Interface Task, 21 hours},
	{Integration into Collaborative Game, 20 hours},
	{AR/VR Task, 34 hours},
	{Research Journal, 7 hours},
	{Self-Directed Study, 24 hours},
	{Self-Directed Studio Practice, 40 hours}}
	
\def\learningSpaceID{1254}